### 2024-04-25 author-kit-CVPR2024-v2/sec/1_intro.tex
updated to PT

\indent In recent years, dance has surged in popularity, whether through TikTok trends in younger 
generations, the growing fanbase for elaborate K-pop dance videos, or the performances in 
reality competition shows (which themselves cover wide genres from ballet and contemporary 
to ballroom dances). As a result of this growing interest, many eager dance novices have 
attempted to self-teach from the abundant dance videos online, available through a variety 
of platforms. However, such individuals often struggle with breaking down movements due to 
the speed or intricacy with which they were executed.
\\
\indent We aim to use Computer Vision to partition dance movements into more easily digestible chunks 
by creating a model that can learn (vectorize) dance choreography from a given dance video, and 
output it in a more human-readable form, such as by describing multiple steps in a motion and 
adding counts or timings for context. By developing a tool that provides detailed descriptions 
of human positions and gestures alongside counts or musical beats, learning dance choreographies 
could become much more accessible and approachable for a broader audience.

%-------------------------------------------------------------------------
\subsection{Existing Attempts}
\indent Several existing attempts have been made to tackle the challenge of learning dance from online 
videos, each with its own approach and limitations. One such approach involves platforms that 
generate reskinned versions of dance performances, offering visual references for users. These 
platforms overlay graphics or animations onto the original video, highlighting key movements or 
positions to provide guidance. While these reskinned versions serve as visual aids, they 
typically do not offer active instruction or detailed breakdowns of the dance steps. As a result, 
users may struggle to fully grasp the nuances and intricacies of the movements, limiting the 
effectiveness of this approach as a learning tool.
\\
\indent Another example is a DancePal Hackathon project, which adopts a more technical approach by 
comparing an ideal video with the end user's video skeletons\cite{Authors14c}. This method involves analyzing the 
skeletal poses extracted from both videos and identifying discrepancies between them. While this 
approach has the potential to provide personalized feedback to users based on their own performances, 
it comes with several challenges. Firstly, it requires an ideal video with specific lighting, 
background, and perspective conditions to serve as a reference, which may not always be feasible 
to obtain. Additionally, accurately mapping movements onto predefined definitions can be difficult, 
especially for complex dance sequences with varying styles and interpretations. As a result, the 
effectiveness of this approach may be limited by the availability of suitable reference videos and 
the accuracy of the mapping process.
\\
\indent Unlike reskinned versions of dance performances, our proposed method provides detailed instructional 
breakdowns of dance movements, guiding learners through each step with clarity and precision. This 
active instruction facilitates better understanding and retention of choreography. Additionally, our 
method could be expanded to offer personalized feedback based on the analysis of the learner's own 
video and that of an original dance video, ideally without the requirement for perfect lighting or 
camera angle conditions.

\subsection{Useful Techniques}
\indent Several computer vision techniques offer promising avenues for addressing the challenge of learning 
dance from online videos by providing deeper insights into the dynamics and nuances of dance 
movements. One such technique involves exploring 3D models instead of traditional 2D skeletonization
 methods to create more comprehensive representations of dance movements. Unlike 2D skeletonization, 
 which captures only the spatial coordinates of key body joints in a single plane, 3D modeling 
 techniques can capture the full spatial extent of movements, including depth information\cite{Alpher03}. This 
 allows for a more accurate and detailed representation of the dancer's body and movements in 
 three-dimensional space, which is particularly valuable for capturing complex and multi-dimensional 
 dance choreographies\cite{Authors14b}.
\\
\indent In addition to 3D modeling, other computer vision techniques such as action recognition, pose 
estimation, trajectory analysis, and video segmentation and tracking can provide valuable insights 
into the dynamics of dance movements. Action recognition algorithms can automatically identify and 
classify different dance gestures and sequences, allowing for automated analysis of choreographic 
patterns and styles. Pose estimation techniques can accurately estimate the skeletal poses of 
dancers from video frames, providing a structural representation of their movements that can be 
used for further analysis and interpretation.
\\
\indent Trajectory analysis techniques can track the trajectories of specific body parts or movements 
over time, allowing for the analysis of movement patterns, velocities, and accelerations\cite{Alpher02}. This 
can provide valuable insights into the rhythmic and dynamic aspects of dance performances, 
helping learners to better understand the timing and pacing of movements. Video segmentation and 
tracking methods can segment dance videos into individual sequences or movements, allowing for more 
focused analysis and comparison of specific choreographic elements.
\\
\indent By leveraging these advanced computer vision techniques, learners can gain a deeper understanding 
of the dynamics and nuances of dance movements, facilitating more effective learning experiences. 
These techniques can help learners to break down complex choreographies into smaller, more 
manageable components, identify areas for improvement, and refine their technique with greater 
precision and accuracy. Overall, the integration of computer vision into dance learning has the 
potential to revolutionize the way dance is taught and learned, making it more accessible, engaging, 
and effective for dancers of all levels.

\subsection{Challenges}
\indent Several challenges arise from attempting this project. One is the quality of input data, which 
encompasses various factors such as lighting, angles, occlusions, frame rates, and blurring. These 
factors can significantly impact the accuracy of movement analysis, as they can obscure or distort 
key visual information needed for understanding dance movements. Addressing these challenges may 
require the development of robust computer vision algorithms capable of handling noisy or low-quality 
video data, as well as techniques for preprocessing and enhancing the visual information to improve 
analysis accuracy.
\\
\indent Moreover, handling interactions between multiple dancers in an ideal video presents additional 
complexities in accurately capturing and representing dance movements. In many dance performances, 
especially group or partner dances, dancers may interact with each other in complex ways, such as 
lifts, partner work, or coordinated movements. Capturing these interactions and accurately 
representing them in the analysis poses challenges for computer vision algorithms, as they must be 
able to differentiate between individual dancers and track their movements independently while also 
accounting for their interactions with others. Addressing this challenge may require the development 
of advanced tracking and segmentation techniques capable of accurately identifying and tracking 
multiple dancers in a crowded or dynamic environment.
\\
\indent Overall, addressing these challenges requires a multidisciplinary approach that combines expertise 
in computer vision, dance analysis, and human-computer interaction. By developing robust algorithms, 
incorporating domain-specific knowledge, and leveraging advanced techniques for handling complex 
visual data, it is possible to create a tool that effectively supports learning dance from online 
videos using computer vision. However, continued research and development efforts are needed to 
overcome these challenges and realize the full potential of computer vision technology in the 
field of dance education.

\subsection{Technical Gap}
\indent The primary aim of this project is to reduce the technical gap between online dance learning resources and 
effective dance instruction. By enabling the correspondence between individuals with different body proportions 
captured from various angles, this tool seeks to enhance the accessibility and inclusivity of dance education. 
This interdisciplinary endeavor involves collaboration between experts in dance, biomechanics, and computer 
vision, with computer vision providing quantitative analysis capabilities to enhance the understanding and 
teaching of dance movements.
\\
\indent In conclusion, developing a tool for learning dance from online videos using computer vision holds 
great potential for revolutionizing dance education and making it more accessible to a wider 
audience. By leveraging advanced computer vision techniques and interdisciplinary collaboration, 
this project aims to bridge the gap between online dance resources and effective dance instruction, 
ultimately empowering individuals to learn and appreciate dance in new and innovative ways.

>>>>

\indent Over 50 million Americans seek physical therapy every year, whether that be from 
musculoskeletal conditions, car accidents, or sports injuries. Evidently, there is a large
need for physical therapy. However, only 35% of PT patients actually adhere to their assigned 
plan. This is a significant problem since the majority of patients are not following 
through with their exercises and thus decrease the effectiveness of their therapy plan.
\\
\indent We aim to use Computer Vision to partition each exercise movement into more easily digestible chunks 
by creating a model that can learn (vectorize) each exercise movement from two given videos, an instructional 
one and a patient one, and compare the two. By developing a tool that provides feedback as a result of analyzing 
the two videos, which ideally should match perfectly, adhering to an exercise plan 
becomes much more feasible, enjoyable, and even motivating.

%-------------------------------------------------------------------------
\subsection{Existing Attempts}
\indent Several existing attempts have been made to tackle the challenge of improving patient adherence, 
each with its own approach and limitations. One such approach involves utilizing monitoring technology, 
such as pedometers, which have proved to be user-friendly. Though such monitoring technologies are 
able to monitor, or track, the patients' physical activity decently well, there was not much of an effect in terms 
of improving their adherence to their exercise plans. As a result, patients using such technologies still struggle with 
adhering to their exercise plans.
\\
\indent Another attempt that has been made is virtual and augmented reality treatment. Through this method, patients 
are able to put on their VR headsets and transport into any environment they would like to complete their exercises in. 
The possibilities are endless: they could surround themselves in peaceful, serene nature, or they could 
opt for a more competitive gaming atmosphere. Physical therapists have found that this actually 
makes their treatment plans more appealing and thus improves their patient adherence rates. However, 
it is important to note that this is significantly more expensive. The cost associated with this 
method is typically too high for the majority of patients and thus makes this approach less practical.
\\
\indent Unlike the aforementioned methods, our proposed method is low-cost, accessible, and effective. 
Implementing the aspect of gamification allows for physical therapy to be fun yet productive. Patients become 
competitors, working hard to beat their previous scores. Additionally, our method could be expanded to offer 
further personalized feedback based on the analysis of the learner's own video and the given instructional video, 
ideally without the requirement for perfect lighting or camera angle conditions.

\subsection{Useful Techniques}
\indent Several computer vision techniques offer promising avenues for addressing the challenge of learning 
exercising movements from instructional videos by providing deeper insights into their dynamics and nuances. 
One such technique involves exploring 3D models instead of traditional 2D skeletonization
 methods to create more comprehensive representations of the exercise movements. Unlike 2D skeletonization, 
 which captures only the spatial coordinates of key body joints in a single plane, 3D modeling 
 techniques can capture the full spatial extent of exericse movements, including depth information\cite{Alpher03}. This 
 allows for a more accurate and detailed representation of the individual's body and movements in 
 three-dimensional space, which is particularly valuable for capturing complex and multi-dimensional 
 exercise movements\cite{Authors14b}.
\\
\indent In addition to 3D modeling, other computer vision techniques such as action recognition, pose 
estimation, trajectory analysis, and video segmentation and tracking can provide valuable insights 
into the dynamics of exercise movements. Action recognition algorithms can automatically identify and 
classify different gestures and even exercise sequences, allowing for automated analysis of exercise 
patterns and styles. Pose estimation techniques can accurately estimate the skeletal poses of 
people from video frames, providing a structural representation of their movements that can be 
used for further analysis and interpretation.
\\
\indent Trajectory analysis techniques can track the trajectories of specific body parts or exercise movements 
over time, allowing for the analysis of exercise movement patterns, velocities, and accelerations\cite{Alpher02}. This 
provides valuable insights into the dynamic aspects of these exercises, 
helping learners to better understand the timing and pacing of the movements. Video segmentation and 
tracking methods also serve to segment the videos into individual sequences or movements, allowing for more 
focused analysis and comparison of specific elements.
\\
\indent By leveraging these advanced computer vision techniques, learners can gain a deeper understanding 
of the dynamics and nuances of exercise movements, facilitating more effective learning experiences. 
These techniques can help learners to break down complex movements into smaller, more 
manageable components, identify areas for improvement, and refine their technique with greater 
precision and accuracy. Overall, the integration of computer vision into physical therapy has the 
potential to revolutionize the way patients approach their recovery plan, making it more accessible, engaging, 
and effective for patients of all levels.

\subsection{Challenges}
\indent Several challenges arise from attempting this project. One is the quality of input data, which 
encompasses various factors such as lighting, angles, occlusions, frame rates, and blurring. These 
factors can significantly impact the accuracy of movement analysis, as they can obscure or distort 
key visual information needed for understanding exercise movements. Addressing these challenges may 
require the development of robust computer vision algorithms capable of handling noisy or low-quality 
video data, as well as techniques for preprocessing and enhancing the visual information to improve 
analysis accuracy.
\\
\indent Moreover, handling interactions between multiple persons in an input video presents additional 
complexities in accurately capturing and representing exercise movements. In some videos, 
there may be two individuals present that interact with each other in complex ways. It is not uncommon for  
one to assist the other in certain movements, for example, by helping lift up or stretch their legs. 
Capturing these interactions and accurately representing them in the analysis poses challenges for 
computer vision algorithms, as they must be able to differentiate between individuals 
and track their movements independently while also accounting for their interactions with others. 
Addressing this challenge may require the development of advanced tracking and segmentation techniques 
capable of accurately identifying and tracking multiple persons in a dynamic environment.
\\
\indent Overall, addressing these challenges requires a multidisciplinary approach that combines expertise 
in computer vision, exercise analysis, and human-computer interaction. By developing robust algorithms, 
incorporating domain-specific knowledge, and leveraging advanced techniques for handling complex 
visual data, it is possible to create a tool that effectively supports learning exercises from  
videos using computer vision. However, continued research and development efforts are needed to 
overcome these challenges and realize the full potential of computer vision technology in the 
field of physical therapy.

\subsection{Technical Gap}
\indent The primary aim of this project is to reduce the technical gap between physical therapy videos and 
effective recovery plans. By enabling the correspondence between individuals with different body proportions 
captured from various angles, this tool seeks to enhance the accessibility and inclusivity of these exercises plans. 
This interdisciplinary endeavor involves collaboration between experts in physical therapy, biomechanics, and computer 
vision, with computer vision providing quantitative analysis capabilities to enhance the understanding and 
teaching of exercise movements.
\\
\indent In conclusion, developing a tool for learning exercises from physical therapy videos using computer vision holds 
great potential for revolutionizing physical therapy plans and making them more accessible and doable to a wider 
audience. By leveraging advanced computer vision techniques and interdisciplinary collaboration, 
this project aims to bridge the gap between physical therapy videos and effective recovery plans, 
ultimately empowering individuals to learn and appreciate physical therapy in new and innovative ways.
